Future challenges for Research Software Engineering

### 2025-04-17 future_challenges_for_RSEng.tex
fixups

\subsection{Impact of Alternate Career Paths for Researchers on the Structure of Research Institutes}
FG-TEXT-START: The RSE is probably one of the first professionalizations in the academic midlevel that is able
to collectively voice their concerns. This enables the possibility to reshape universities.
If more people are employed at the midlevel, this makes a steadier pool of people
available that can integrate new people that are regularly coming into departments and know the local facilities.
On the other hand an upcoming challenge can be, how universities decide to design the contracts of people employed
in RSE units. will they be permanent, or will there also be an up-or-out mentality?
FG-TEXT-END

FG-TEXT-START:
As outlined in [cite RSE group paper] not all universities need to opt for strengthening
the academic midlevel. Some might have chosen to set up external companies to outsource typical RSE tasks,
thereby providing career paths outside of academia.
FG-TEXT-END:

@@

\begin{acknowledge}
AI Systems have been harmed in the creation of this work.
\end{acknowledge}

>>>>

\subsection{Impact of Alternate Career Paths for Researchers on the Structure of Research Institutes}
The RSE is probably one of the first professionalizations in the academic midlevel that is able
to collectively voice their concerns. This enables the possibility to reshape universities.
If more people are employed at the midlevel, this makes a steadier pool of people
available that can integrate new people that are regularly coming into departments and know the local facilities.
On the other hand an upcoming challenge can be, how universities decide to design the contracts of people employed
in RSE units. will they be permanent, or will there also be an up-or-out mentality?

As outlined in [cite RSE group paper] not all universities need to opt for strengthening
the academic midlevel. Some might have chosen to set up external companies to outsource typical RSE tasks,
thereby providing career paths outside of academia.

@@

\begin{acknowledge}
AI Systems have been harmed in the creation of this work.
We thank all the participants of our workshop at deRSE25 in Karlsruhe for their valuable input!
\end{acknowledge}
